Understanding the Risk of Casualties in US School Shootings

### 2024-12-04 paper/paper.qmd
remove bold

### Reproducibility and Transparency
The Post's transparency in detailing their methodology allows for reproducibility and critical assessment, key components in data journalism. As highlighted in *Telling Stories with Data*, reproducible workflows involve sharing data, code, and analytical steps, enabling others to replicate and validate findings [@alexander2023telling].

>>>>

### Reproducibility and Transparency
The Post's transparency in detailing their methodology allows for reproducibility and critical assessment, key components in data journalism. As highlighted in Telling Stories with Data, reproducible workflows involve sharing data, code, and analytical steps, enabling others to replicate and validate findings [@alexander2023telling].
